Yelp Academic Dataset Final Report

### 2016-08-09 paper/paper.Rmd
final version updated

The mean rating was 3.718 for unfamiliar and 3.762 for familiar places. However, the standard deviation for the familiar locations plot was 0.41, and unfamiliar one was 1.37 so star rating, explained by the variablity between users who travelled.

>>>>

However, it was interesting to see that the mean rating was 3.718 for unfamiliar and 3.762 for familiar places. They were almost equal to each other despite of such user's behavioral changes on familiarity with the location.
